R Notebook

### 2021-07-27 Paper_Figure_code.Rmd
Upgrades
Fix according to comments on figure 5 & 6

p_GSE132203_100_BPmet_all <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6, 5)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

p_GSE132203_100_BPmet_all_longly <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~"BPmet") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6, 5)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

@@

p_GSE132203_100_BPmet[[1]] <- ggplot(melt_GSE132203_100_BPmet[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[2]] <- ggplot(melt_GSE132203_100_BPmet[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.42, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.075, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[3]] <- ggplot(melt_GSE132203_100_BPmet[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.074, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[4]] <- ggplot(melt_GSE132203_100_BPmet[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.248, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.050, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[5]] <- ggplot(melt_GSE132203_100_BPmet[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[6]] <- ggplot(melt_GSE132203_100_BPmet[[6]], aes(x = value, y = V)) +
  geom_point(colour = c("deepskyblue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.82, size = 6) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  annotate("text", x = 0.26, y = 0.68, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)

@@

p_GSE132203_100_MethylCIBERSORT_WB_all <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4, 9)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

p_GSE132203_100_MethylCIBERSORT_WB_all_lonly <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~"MethylCIBERSORT") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, labels = NULL, breaks = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4, 9)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
#### each cell types

@@

p_GSE132203_100_MethylCIBERSORT[[1]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL) +
  scale_y_continuous(name = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.245, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.078, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[2]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.335, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.0772, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[3]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.335, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.077, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[4]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black") +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.052, y = 0.135, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)

>>>>

p_GSE132203_100_BPmet_all <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6, 5)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

p_GSE132203_100_BPmet_all_longly <- ggplot(melt_GSE132203_100_BPmet, aes(x = FACS, y = ALL, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"BPmet") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.95), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(2, 3, 4, 1, 6, 5)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

@@

p_GSE132203_100_BPmet[[1]] <- ggplot(melt_GSE132203_100_BPmet[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.078, y = 0.27, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[2]] <- ggplot(melt_GSE132203_100_BPmet[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.5, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.42, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.075, y = 0.34, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[3]] <- ggplot(melt_GSE132203_100_BPmet[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.33, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.074, y = 0.26, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[4]] <- ggplot(melt_GSE132203_100_BPmet[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.3)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.248, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.050, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[5]] <- ggplot(melt_GSE132203_100_BPmet[[5]], aes(x = value, y = V)) +
  geom_point(colour = c("darkmagenta"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.15)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", 0.039, y = 0.14, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[5], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_BPmet[[6]] <- ggplot(melt_GSE132203_100_BPmet[[6]], aes(x = value, y = V)) +
  geom_point(colour = c("deepskyblue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 1, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.82, size = 6) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  annotate("text", x = 0.26, y = 0.68, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[6], 2))))), parse = TRUE, size = 6)

@@

p_GSE132203_100_MethylCIBERSORT_WB_all <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"ALL") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, limits = c(0, 1)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4, 9)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)

p_GSE132203_100_MethylCIBERSORT_WB_all_lonly <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB, aes(x = FACS, y = MethylCIBERSORT, colour = cell_type)) +
  geom_point(shape = 19, size = 4) +
  theme_bw() +
  scale_color_manual(values = c("red", "green", "blue", "darkgoldenrod1", "darkmagenta", "deepskyblue")) +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~"MethylCIBERSORT") +
  scale_x_continuous(name = NULL, limits = c(0, 1)) +
  scale_y_continuous(name = NULL, labels = NULL, breaks = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(legend.justification = c(0.05, 0.95), legend.position = c(0.05, 0.96), legend.title = element_blank(), legend.key.size = unit(0.8, "cm"), legend.background = element_rect(fill = "transparent")) +
  annotate("text", x = 0.6, y = 0.15, label = paste("R = ", round(cor.test(out.l$estF[, c(3, 5, 1, 2, 4, 9)], FACS_GSE132203_100)$est, 3)), parse = F, size = 8)
#### each cell types

@@

p_GSE132203_100_MethylCIBERSORT[[1]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[1]], aes(x = value, y = V)) +
  geom_point(colour = c("red"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL) +
  scale_y_continuous(name = NULL) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.3, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.245, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.078, y = 0.2, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[1], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[2]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[2]], aes(x = value, y = V)) +
  geom_point(colour = c("green"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.335, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.0772, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[2], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[3]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[3]], aes(x = value, y = V)) +
  geom_point(colour = c("blue"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.3)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.4)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.4, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.335, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.077, y = 0.275, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[3], 2))))), parse = TRUE, size = 6)

p_GSE132203_100_MethylCIBERSORT[[4]] <- ggplot(melt_GSE132203_100_MethylCIBERSORT_WB[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = c(0, 0.2)) +
  scale_y_continuous(name = NULL, limits = c(0, 0.2)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 16, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.2, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.165, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.052, y = 0.135, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)
